\section{Sheet 1}
\input{foundrep/sol1}
\hrule
\begin{prop}
Let $k$ be a field, $k[X]$ the polynomial ring and $p\in k[X]$ a polynomial with $\deg p=n$. Then
	\[
	k[X]/(p)
	\]
is a $n$-dimensional $k$ vector space, and a basis is given by
	\[
	\{1,x,...,x^{n-1}\}.
	\]
\end{prop}
The following propositions are taken from \cite{aluffi}.\\
Let $R$ be any commutative ring.
\begin{prop}
  Let $I_1,...,I_k$ be ideals of $R$ such that $I_i+I_j=(1)$ for all $i\neq j$. Then the natural homomorphism
  \[
  \pphi :R\to R/I_1\times \hdots \times R/I_k
  \]
  is surjective and induces an isomorphism
  \[
  \frac{R}{I_1\hdots I_k}\to R/I_1\times \hdots \times R/I_k
  \]
\end{prop}
\begin{cor}[Chinese remainder theorem]
  Let $R$ be a PID and $a_1,...,a_k\in R$ be elements such that $\gcd(a_i,a_j)=1$ for all $i\neq j$. Let $a=a_1\hdots a_k$. Then the function
  \[
  \pphi: R/(a)\to R/(a_1)\times \hdots \times R/(a_k).
  \]
\end{cor}
\begin{prop}[Yoneda Lemma\index{Lemma!Yoneda}]
	Let $\cat{C}$ be a category, $X$ an object of $\cat{C}$ and consider the contravariant functor
	\[
	h_X:= \hom_{\cat{C}}(-,X).
	\]
	Then for every contravariant functor $\fcr{F}:\cat{C}\to \cat{Set}$, there is a bijection between the set of natural transformations $h_x\nattraf\fcr{F}$ and $\fcr(X)$.
\end{prop}
\begin{defn}[\cite{assem1}]
	The (Jacobson) \emph{radical} $\rad A$ of a $K$-algebra $A$ is the intersection of all maximal right ideals in $A$. It is the same as the intersetion of all left-sided maximal right ideals in $A$. Furthermore, $\rad A$ is a two-sided ideal.
\end{defn}

\begin{defn}
	Let $f,g:X\to Y$ be morphisms in a category $\cat{C}$. Then a morphism $e:E\to X$ is called \emph{equalizer} of $f$ and $g$ if $f\circ e=g\circ e$ and for all other morphisms $o:O\to X$, such that $f\circ o=g\circ o$, there is a unique morphis $O\to E$, such that the following diagram commutes:
	\[
	\begin{tikzcd}
		E\ar{r}{e}&X\ar[shift left = .5ex]{r}\ar[shift right = .5ex]{r}&X\\
		O\ar[dashed]{u}{\exists !}\ar{ur}{o}&&.
	\end{tikzcd}
	\]
\end{defn}
\begin{prop}
	Equalizers exists in abelian categories.
\end{prop}
\hrule
\subsection*{Task 1}
See this as a functors:
\[
\begin{tikzcd}k\mdas\alc \ar[shift left]{r}{\fcr{V}}\ar[shift right, swap,leftarrow]{r}{\fcr{A}}&\grpc\end{tikzcd}
\]
Grp. alg. construction $\fcr{A}$ is left-adjoint to group of units construction $\fcr{V}$.
\begin{enumerate}
	\item Show that there is a natural isomorphism
	\[
	k\mdas\alc(\fcr{A}(G),A) \cong \grpc(G,\fcr{V}(A))
	\]
	for all groups $G$ and $k$-algebras $A$.
\end{enumerate}
\subsection*{Task 2}
This quiver is called the \emph{linear oriented quiver}\index{quiver!linear oriented}.
Define
\[
\pphi:KQ\to\lowtri_n(k)
\]
as linear extension of the $k$-linear map
\[
Q\bast\to \lowtri_n(k),~p_{ij}\mapsto (E_{ij}){kl}:= \begin{cases}1&\text{if }k=i,l=j\\0&\text{otherwise}\end{cases}
\]
This is indeed a homomorphism of $k$-algebras, which sends basis vectors to basis vectors.\par
\subsection*{Task 3}
Let $\ccat,\dcat$ be two \emph{$k$-linear} categories \index{category!linear}, i.e. $\ccat(X,Y)$ has the structure of a $k$-vector space and composition is bilinear. We say that $\ccat$ is \emph{equivalent} to $\dcat$ ($\ccat \simeq \dcat$) if there are \emph{$k$-linear} functors
\[
\ffunc :\ccat \to \dcat \text{ and }\gfunc:\dcat \to \ccat
\]
(i.e. functors that induce $k$-linear maps $\ccat(X,Y)\to \dcat(\ffunc(X),\gfunc(Y))$, and for $\gfunc$ analogous), such that there are natural isomorphisms
\[
\gfunc \ffunc \simeq \idfunc_{\ccat}\text{ and }\ffunc \gfunc \simeq \idfunc_{\dcat}
\]
\begin{thm}
	Let $\ccat,\dcat$ be $k$-linear categories. $\ccat \simeq \dcat$ if and only if there is a fully faithful, $k$-linear and dense functor
	\[
	\ffunc: \ccat \to \dcat .
	\]
\end{thm}
\begin{rem}
	The proof is supposed to only invoke the Axiom of Choice, and should work for general $\hom$-Sets.
\end{rem}
This task basically shows that there is an equivalence of categories
\[
\repc(A)\simeq k\mdas \mdc(A),
\]
where
\[
\repc(A):= \{(V,\pphi)\ssp V\text{ a }k\mdas\text{vector-space, }\pphi:A\to \eno_{k}(V)\text{ a algebra-homomorphism}\}
\]
Calvin highly recommends the book \cite{assem1}.
